Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-13 article/article.tex
Commit 2024-06-13 19:11

The main focus of this study is to investigate the time evolution of the
CE events by analyzing the GHI measurements at Thessaloniki. Cloud
enhancements can be influenced by different factors, such as the
geometry, size and optical thickness of clouds, their height in the
atmosphere and on local weather regimes \textbf{!!!(ref)!!!}. Some of
these factors are related to changes in climate; hence it would be
reasonable to expect capturing their contributions to the frequency of
occurrence of CE events over Thessaloniki, as well as to the average OIR
and excess irradiation. The long-term trends were calculated using a
first-order autoregressive model with the `maximum likelihood' fitting
method \citep{Gardner1980, Jones1980}, by implementing the function
`arima' from the library `stats' of the R programming language
\citep{RCT2023}. All trends are reported together with their \(2\sigma\)
error.

>>>>

The main focus of this study is to investigate the time evolution of the
CE events by analyzing the GHI measurements at Thessaloniki. Cloud
enhancements can be influenced by different factors, such as the
geometry, size and optical thickness of clouds, their height in the
atmosphere and on local weather regimes
\citep{Mol2023, Veerman2022, Gristey2022, Tzoumanikas2016}. Some of
these factors are related to changes in climate; hence it would be
reasonable to expect capturing their contributions to the frequency of
occurrence of CE events over Thessaloniki, as well as to the average OIR
and excess irradiation. The long-term trends were calculated using a
first-order autoregressive model with the `maximum likelihood' fitting
method \citep{Gardner1980, Jones1980}, by implementing the function
`arima' from the library `stats' of the R programming language
\citep{RCT2023}. All trends are reported together with their \(2\sigma\)
error.
